Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-03 sections/correlated-sicm-and-fm.tex
First paragraphs reviewed

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
This is especially helpful for applications, where the reaction is not limited to \emph{one 
dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
be interesting to investigate, sowohl %german
the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
\cite{Hansma1989} --, als auch %german
to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.

% Den Teil brauchen wir ja vielleicht nicht. 
AFM, a method belonging to the scanning probe microscopy techniques, was successfully
combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
with this method is, that it is not the most favorable for investigating living cells in their
physiological surrounding. Certain destructive effects on the cell were found by using this 
technique \cite{}. A better fitting method for investigating living cells would be scanning 
ion conductance microscopy (SICM) \cite{Hansma1989}.

@@

In addition, hippocampal neurons, which were very delicate samples with many little protrusions, 
could be investigated with correlated SICM and confocal microscopy. With such a combination active
synaptic boutons could be identified \cite{Novak2013} or the topography could be correlated with 
the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2020}.

@@

Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
could be also used for nanoinjection of fluorescently labeled molecules into living cells 
\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and direct stochastic 
optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
introduced into the membranes, could occur \cite{Hennig2015_nanoinj}.

@@

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors 
\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
After measuring the topography (SICM) the nanopipette could be moved to places -- e.g. the 
z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} -- where the 
adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
conformation and a FRET signal could be detected \cite{Nikolaev2010}.

@@

By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
even Rheinberg illuminations were possible \cite{Webb2015}.

>>>>

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and FM, despite the mismatch in resolution, allows to gather
information which cannot be obtained by using a single technique
alone. However, the degree of correlation differs, depending on the FM
technique combined with SICM. Combining SICM and wide-field FM allows to image
the same region of the sample, which, for example, can be used to find a
region of interest such as an area containg synapses in a culture of a
neuronal network \cite{Novak2013,Scheenen2015}.

% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
% Fluoreszenz sehen kann.

% This is especially helpful for applications, where the reaction is not limited to \emph{one 
% dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
% be interesting to investigate, sowohl %german
% the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
% \cite{Hansma1989} --, als auch %german
% to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
% react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.

% % Den Teil brauchen wir ja vielleicht nicht. 
% AFM, a method belonging to the scanning probe microscopy techniques, was successfully
% combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
% cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
% with this method is, that it is not the most favorable for investigating living cells in their
% physiological surrounding. Certain destructive effects on the cell were found by using this 
% technique \cite{}. A better fitting method for investigating living cells would be scanning 
% ion conductance microscopy (SICM) \cite{Hansma1989}.

@@

In addition, hippocampal neurons, which were very delicate samples with many little protrusions, 
could be investigated with correlated SICM and confocal microscopy. With such a combination active
synaptic boutons could be identified \cite{Novak2013} or the topography could be correlated with 
the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2019}.

@@

Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
could be also used for nanoinjection of fluorescently labeled molecules into living cells 
\cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
introduced into the membranes, could occur \cite{Hennig2015a}.

@@

SICM in combination with Förster resonance energy transfer (FRET) sensors could be used for
the localisation of $\beta_{1}$-adrenoceptors \cite{Wright2018}, $\beta_{2}$-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and $\beta_{3}$-adrenoceptors 
\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
After measuring the topography (SICM) the nanopipette could be moved to places -- e.g. the 
z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} -- where the 
adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
conformation and a FRET signal could be detected \cite{Nikolaev2010}.

@@

By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
even Rheinberg illuminations were possible \cite{Webb2014}.
